% Created 2013-02-12 Tue 22:48
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\addtolength{\textwidth}{2in}
\addtolength{\hoffset}{-1in}
\providecommand{\alert}[1]{\textbf{#1}}

\title{Reprev}
\author{Singers In Accord}
\date{Feb. 12, 2013}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs Org-mode version 7.9.3d}}

\begin{document}

\maketitle


\section{7:20 [10 mins]  Debrief on cancellation decision.  Great communication execution w/text messaging!}
\label{sec-1}


Dan talked about how the decision was made, including talking with the
board and Peter.  The thought was that many audience members would
have stayed home anyway, making for a possibly low-reward concert.
\section{7:30 [10 mins] Concert.  How did we like music, location, school performance?}
\label{sec-2}


Gerald: Thought it went well.  Several latino/latina people in the
audience.

Kim: Liked the venue.  School choir blew me away.  School choir also
gave us an audience.

Becky: it's nice to have a chance to walk off the stage \& sit for a
couple songs too.

Shelby: it was tough to make it so far away

Rosalie: the school choir was envious of our bass section.
\section{7:40 [10 mins] Peter.  How did we like him?  Style, preparation, etc.}
\label{sec-3}


Bill: was disappointed in Peter's command of the music.  Often gave
incorrect pronunciation, rhythm, didn't have good rehearsal plans.

Becky: was disappointed in Peter's non-use of Bill as rehearsal
assistant.  Would have been very helpful.

Phil: agree - but keep in mind that he was rehearsing us for an a
cappella concert, and we needed to have less piano.

Kathie: yes, BUT, his approach is less technical, more ``feeling it''.

Monica: thought it was fun overall.  We're adaptable, and it's fine
for us to adapt.

Gloria: wasn't on board with the layered approach to learning.

Ken: there was tension with Bob's readiness, Peter seemed to be tense
about it not working well too.

Joe: some issues might have been caused by the music selection.

Mike Mc: it was a mistake to not do language/pronunciation earlier.

Schele: yeah, but it was all fun!

Judy: it was frustrating to try to memorize Hanacpachap but not do it
from memory.

Gloria: we should have considered more before we agreed to memorize.
Some of us knew it was going to be too hard.

Schele: did we like the music?  Did we like doing an a cappella
program?

Angela: yes, very fun.

Joe: my family liked it but couldn't really differentiate one song
from another.

Rosalie: was a lot of our unpreparedness stemming from our absences,
and not preparing enough early enough?

Kathie: we should really get the foreign-language text recorded \&
available earlier.

Schele: I'm hearing that the group has high choral standards, and we
don't enjoy it if the director wants us to ``relax'' about something.
It may help to limit the amount of music and do it better, like we
always talk about.

Schele: let the record reflect that it seemed like no big deal to do a
whole concert of a cappella music.

Mike McC: it was way more satisfying to do this music with this group
than it was, e.g., with World Voices, who always sounded Norwegianish.

Vote: about 60\% would like to work again with Peter, about 40\% would
rather not.
\section{7:50 [10 mins] How do we sound?  Recruiting.  Attendance (Dan)}
\label{sec-4}

   Outside practice. How can we do our part for quality?  Should we
   try to avoid a T/Th/S/Sun final week?  Or does the Thursday
   practice help?

Attendance: it sort of fell apart a little bit, people don't
necessarily follow the absence reporting protocols.

Dan: almost all of our absences came in the first 4 rehearsals.  We
got behind the 8 ball because of it.

Kim: was really frustrated with choir chatter, and asking too many questions.

Ken: most of the chatter is people ``trying to be helpful'' and
straightening out their parts.  But it hurts the rest of us.
\section{7:55 [5 mins] Financial. (Mike/Dan) How did we do?}
\label{sec-5}


220 people at concert.  Took in \$831 on Saturday tickets, with \$1000
in donations.  Net cost was \$3400 to put on the concert.
\section{8:00 [5 mins] Audience/marketing - Postcards/Posters/Facebook.}
\label{sec-6}

   Appeal for more database names.
\section{8:05 [5 mins] Thank Yous - Concert organizers, music, attendance, etc.  Give visibility to the SIA volunteers.}
\label{sec-7}


Brent/Rachel for concert coordination

Penny for marketing/programs

Jan for doing all the percussion and keeping the section together

Bill: really enjoyed doing the concert

Sheri for keeping marketing/financial database

Mike McC for taking the photo for the program

Ken for the recordings stuff

Etta for doing the rehearsal notes

Rachel L. for doing marketing work

Rachel C. for doing librarian stuff
\section{8:15 [10 mins] Next Concert (Dan/Jan)}
\label{sec-8}


Double whammy - Joshua Jacobson \& Judy Sagen.  Judy's well known \&
high energy.

Fairly expensive concert to put on, and will charge relatively high
prices for tickets.  There are only 300 seats in the hall, we could
likely sell out both nights.

JJ will also work with several high schools \& colleges.

Got a large grant from the Rimon foundation.

Etta: we're doing a large swath of the Judaic canon.  People should
take a look at the text, many pieces are very powerful.

Dan: concerts are THURSDAY and SUNDAY.  We also have a rehearsal
MONDAY the week of the concert.  MAKE SURE to clear your calendars for
them.

Dan: there's a fair amount of Hebrew to learn, but only about 38
minutes of music, which seems manageable.
\section{8:25 [5 mins] Discussion on dress - Next concert - concert formal attire.  Feedback on ties/scarves?}
\label{sec-9}


Schele: announces formation of committee on attire.

Schele: wants person to be recruiting chair.

Bill/Judy: speaking of recruiting, the new singers are great.

Kim: would like bigger choir, fuller sound.
\section{8:30 [10 mins] Next Season (Dan/Jan)}
\label{sec-10}


Discuss idea of ``mini'' winter concert?  Recruit more singers so we might have an option to take an occasional concert off?

Gloria: loves the idea

Bill: loves the idea.  would like to organize a recital too.

Rosalie: was resistant when she heard the idea before, but now is
warming to it.

Tad: maybe a recording session in the interim?

Judy: we could produce a YouTube recording too

Ken: are there people who would be really disappointed by dropping a
concert?  We need to hear now.

Kim: the idea is saved by doing interim projects

Dan T: does it limit our exposure in the community to only do 2
concerts?

Tad: Dan T. is about to be a father, by the way.

Rachel: would ease the burden on the marketing team

Shelby: we could take things on the road to cultural centers.

Gloria: audience burnout.
\section{8:40 [5 mins] (Ken) iPad review}
\label{sec-11}


Ken showed how the ForScore app works on the iPad.

\end{document}
